Factors influencing Total Income in the United States

### 2024-12-03 paper/paper.qmd
Adjust Paper

\begin{align*}
\hat{\text{income}} &= \beta_0 + \beta_1 \cdot \text{Sexmale} + \beta_2 \cdot \text{Education Level} + \beta_3 \cdot \text{Marital Status} + \beta_4 \cdot \text{Labor Force} \\
&\quad + \beta_5 \cdot \text{num\_work} + \beta_6 \cdot \text{num\_occu}
\end{align*}

```{r}
#| label: fig-lm
#| fig-cap: Linear Model has limited predictive accuracy for Total Income
#| echo: false
#| warning: false
#| message: false
lm_model <- lm(formula = income ~ Sex + educ + married + lf + num_work + num_occu, data = data)
prediction_1<- predict(lm_model, data)

@@

# Draw the table 
kable(table_description, col.names = c("Variable", "Estimate", "Std. Error", "t-value", "Pr($\\gt \\mid t \\mid $)", "Significance")) |>
  kable_styling(latex_options = c("striped", "hold_position"))
```

>>>>

\begin{align*}
\hat{\text{income}} &= \beta_0 + \beta_1 \cdot \text{Sexmale} + \beta_2 \cdot \text{Education Level} + \beta_3 \cdot \text{Marital Status} + \beta_4 \cdot \text{Labor Force} \\
&\quad + \beta_5 \cdot \text{Work Status} + \beta_6 \cdot \text{Occupation Category}
\end{align*}

```{r}
#| echo: false
#| warning: false
#| message: false
lm_model <- lm(formula = income ~ Sex + educ + married + lf + num_work + num_occu, data = data)
prediction_1<- predict(lm_model, data)
```

```{r}
#| label: fig-lm
#| fig-cap: Linear Model has limited predictive accuracy for Total Income
#| echo: false
#| warning: false
#| message: false

@@

# Draw the table 
kable(table_description, col.names = c("Variable", "Estimate", "Std. Error", "t-value", "Pr($\\gt \\mid t \\mid $)", "Significance")) |>
  kable_styling(latex_options = c("striped", "hold_position"))
```
## Log Transformation of Linear Model {#sec-model-log}

## Bayes Model {#sec-model-bayes}

## Bayes Model on Log Transformation {#sec-model-logbayes}
